\section{Design Goals}
\label{sec:design}
The design targets minimal disruption to the Cray PE workflow, reproducibility
for support teams, and portability across Cray/HPE systems. The primary
assumption is that user build systems and support tooling already depend on PE
wrappers and module semantics.

\begin{itemize}
  \item Preserve Cray wrapper semantics while enabling AMD compiler drops.
  \item Keep module interactions deterministic and reversible.
  \item Provide consistent MPI and library metadata via pkg-config.
  \item Support rapid testing with clear diagnostics for support staff.
\end{itemize}

Beyond these goals, the design explicitly targets module-order independence and
diagnostic completeness. Support teams need to reproduce user environments
where libraries may be loaded before or after AFAR, so Afar-prgenv treats
`pkg-config` metadata and wrapper state as dynamic rather than static at module
load time.

\subsection{Readiness Criteria}
\label{sec:readiness}
We define readiness as the ability to compile and link common MPI, OpenMP
offload, and PE library workflows using the standard `ftn/cc/CC` wrappers.
Repro tests are treated as gates: a drop is considered ready for broader
validation only after the repro suite reports PASS for core workflows and
explicitly documents any SKIP conditions. This gating model prioritizes
correctness and compatibility before any performance tuning or application
regression testing.

\subsection{Non-Goals}
\label{sec:nongoals}
We do not replace the Cray PE or provide a new package manager. Instead, we
focus on the narrow but critical gap between AFAR drop availability and PE
integration, prioritizing correctness and compatibility over performance tuning.
