\section{Discussion}
\label{sec:discussion}
We discuss the trade-offs of the overlay approach, portability to other Cray/HPE
systems, and limitations observed during validation.

\subsection{Limitations}
\label{sec:limitations}
The overlay depends on PE wrappers and module hierarchy conventions; changes in
those interfaces require updates to Afar-prgenv. Some vendor libraries ship
Fortran modules that are not compatible with AFAR compilers and require shims
or local builds. Accelerator libraries (e.g., `libsci-acc`) may also lag when
runtime dependencies are tied to older ROCm versions.
Parallel HDF5 validation can also be constrained by missing C++ `pkg-config`
metadata in the PE environment, which must be addressed before full coverage.

We also intentionally avoid performance benchmarking in this work. Our goal is
functional readiness and compatibility; performance evaluation is deferred
until after a drop passes the compatibility gate.

\subsection{Operational Scalability}
\label{sec:scalability}
The combination of a generator-driven module tree and a repro harness makes
monthly AFAR drops tractable for support teams. Most updates are data-driven:
adding a version mapping, regenerating modulefiles, and running the repro
matrix. This workflow scales across multiple drops because the wrapper logic
and `pkg-config` shims are shared, while version-specific differences are
captured in configuration files and module metadata.

\subsection{Portability}
\label{sec:portability}
Afar-prgenv generalizes to other Cray/HPE systems because it leverages the same
PE module hierarchy and wrappers. The system-specific configuration is limited
to the AFAR root path, version mappings, and the Cray MPICH install path, all
of which are captured in configuration files.

Portability is strongest when the target system follows standard Cray PE
conventions for `ftn/cc/CC` and `pkg-config`. Sites with non-standard module
layouts may need additional wrapper filter rules or shim metadata to preserve
order independence.

\subsection{Lessons Learned}
\label{sec:lessons}
Two operational lessons stand out. First, early drop readiness is mostly a
metadata problem: wrapper semantics and `pkg-config` paths must be correct
before any application testing can succeed. Second, reproducible repro tests
are critical for support teams because they isolate regressions to specific
libraries or wrapper behaviors. These lessons inform how we prioritize future
automation and validation.
