\section{Introduction}
\label{sec:intro}
Cray/HPE systems provide a stable programming environment (PE) that couples
compilers, MPI, and optimized libraries behind consistent `ftn/cc/CC` wrappers.
This stability is essential for production workloads, but it slows adoption of
new compiler drops from AMD, particularly when the Cray PE does not yet ship
the corresponding toolchain. Support teams and early adopters are left with a
choice: wait for vendor integration or accept a fragmented environment that
cannot interoperate with PE libraries and tooling.

Afar-prgenv closes this gap.\cite{AfarPrgenv2025} It overlays AMD AFAR compiler and ROCm drops into
the Cray PE module hierarchy while preserving the PE contract that users and
build systems depend on. The overlay provides wrapper logic for OpenMP offload,
MPI metadata re-synchronization, and pkg-config shims that keep library flags
stable even when modules are swapped. The result is a workflow where new drops
can be tested monthly without breaking production tooling, and without requiring
users to abandon the PE conventions they rely on.

\subsection{Contributions}
\label{sec:contrib}
\begin{itemize}
  \item Define the user-support problem for early compiler evaluation on
  Cray/HPE systems and motivate the need for a safe, reversible overlay.
  \item Present the Afar-prgenv design and implementation, including its module
  hierarchy, wrapper behavior, and pkg-config integration.
  \item Evaluate Afar-prgenv on Frontier with representative compile, link,
  and offload workflows, and report operational outcomes for support teams.
\end{itemize}
