\section{Motivation}
\label{sec:motivation}
Frontier and similar Cray/HPE systems evolve rapidly, while vendor-supported
programming environments lag behind emerging AMD compiler and ROCm drops. User
support teams need a mechanism to validate new compiler stacks without
disrupting production workflows or forcing users to rebuild their toolchains
from scratch.

AFAR drops arrive on a roughly monthly cadence. Each drop must be validated for
basic functionality, compatibility with the PE module hierarchy, and correctness
in mixed environments where MPI and vendor libraries are required. Without an
overlay, AFAR drops are effectively isolated: they cannot cleanly consume Cray
libraries or interact with standard build systems that rely on
\texttt{ftn/\allowbreak cc/\allowbreak CC}.
In practice, this makes AFAR drops unusable for production users until a
support tool like Afar-prgenv bridges the gap.

The support burden is amplified by module ordering and metadata coupling.
Users often load library modules before the compiler stack, and `pkg-config`
metadata can become stale when MPI or PE libraries are swapped after a drop is
loaded. These issues are easy to miss in ad hoc testing but cause immediate
failures in user builds. Afar-prgenv is motivated by the need to make drop
evaluation deterministic under real-world module ordering.

\subsection{User Support Challenges}
\label{sec:support-challenges}
Support teams must bridge mismatched compiler/runtime versions, conflicting
modules, and inconsistent compile/link metadata across rapidly changing
software stacks. Even when an AFAR drop compiles user code, it can fail at link
time due to missing PE library metadata or incompatible Fortran modules. These
issues are difficult to triage because the failure surface spans compiler
wrappers, MPI module files, and library search paths.

\subsection{Use Cases}
\label{sec:use-cases}
\begin{itemize}
  \item Early validation of AMD compiler drops against Cray PE workflows.
  \item Compatibility testing for MPI, OpenMP offload, and vendor libraries.
  \item Reproducible support environments for debugging user issues.
\end{itemize}
