\section{Repro Harness and Test Inventory}
\label{sec:harness}
This section details the repro harness used to gate AFAR drops and the catalog
of tests that exercise PE wrapper, MPI, OpenMP, and library integration.

\subsection{Harness Architecture}
\label{sec:harness-arch}
The repro harness is driven by \texttt{scripts/run\_afar\_tests.sh}. It defines
named profiles that extend a baseline PE stack with a specific library module
and then runs every repro under that profile. By default, the harness loads
each library module both before and after \texttt{afar-prgenv} to validate
module-order independence. The ordering can be restricted with
\texttt{--lib-order before|after|both} when a focused regression is needed.

Profiles can be overridden by environment variables so support teams can
validate alternate PE versions or modulepaths without editing the scripts.
Common overrides include \texttt{AFAR\_TEST\_CPE}, \texttt{AFAR\_TEST\_MPICH},
and \texttt{AFAR\_TEST\_MODULEPATH}. The harness also supports targeted
execution through \texttt{--profiles} and \texttt{--keep-going}, enabling
incremental validation when a drop is known to have a single regression.

\subsection{Repro Case Catalog}
\label{sec:harness-catalog}
\begin{table*}[t]
  \centering
  \small
  \setlength{\tabcolsep}{4pt}
  \caption{Repro cases and their validation focus.}
  \label{tab:repro-catalog}
  \begin{tabular}{l p{0.24\textwidth} p{0.55\textwidth}}
    \hline
    Repro & Focus & Requirements/Notes \\
    \hline
    compile-only & Fortran compiler sanity & AFAR `ftn`; no link step. \\
    cmake-mpi-omp & CMake wrapper pass-through & CMake in \texttt{PATH}; uses `ftn` and `cc`. \\
    wrapper-compile-link & Wrapper compile/link split & Uses \texttt{scripts/check\_ldd.sh} on outputs. \\
    mpi-hello & MPI module integration & Requires \texttt{cray-mpich}; \texttt{AFAR\_TEST\_RUN\_MPI} enables runtime. \\
    omp-c & OpenMP offload (C) & Requires \texttt{craype-accel-}\allowbreak\texttt{amd-gfx90a} or \texttt{AFAR\_CC\_OFFLOAD\_ARCH}. \\
    omp-f90 & OpenMP offload (Fortran) & Requires \texttt{craype-accel-}\allowbreak\texttt{amd-gfx90a} or \texttt{AFAR\_FTN\_OFFLOAD\_ARCH}. \\
    libsci & LibSci links & Uses \texttt{pkg-config libsci}. \\
    libsci-acc & LibSci accelerator links & Uses \texttt{AFAR\_LIBSCI\_ACC\_LIBNAME}; skipped if ROCm 6 deps missing. \\
    hdf5 & HDF5 serial/parallel & Uses AFAR-compiled Fortran shim; requires `pkg-config hdf5`. \\
    fftw & FFTW bindings & Uses \texttt{pkg-config fftw3}. \\
    dsmml & DSMML bindings & Uses \texttt{pkg-config dsmml}. \\
    netcdf & PnetCDF bindings & Uses `pnetcdf.inc`; skips Fortran if include is missing. \\
    \hline
  \end{tabular}
\end{table*}

The catalog emphasizes compatibility with PE metadata rather than numerical
performance. Every repro compiles and links via `ftn/cc/CC` to ensure wrapper
semantics remain intact across profiles.

\subsection{Logging and Diagnostics}
\label{sec:harness-logs}
Log files are written under \texttt{logs/} and include a timestamp plus profile
suffix (for example, \texttt{20240320-base.log}); the location can be
overridden with \texttt{AFAR\_TEST\_LOG\_DIR}. These logs
capture wrapper warnings, `pkg-config` paths, and linker diagnostics that
support teams use to triage regressions. For deeper debugging, the wrappers
support \texttt{AFAR\_WRAPPER\_DEBUG} to emit the final argument list passed to
the underlying Cray PE drivers.
